Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-27 snapshot_system/fast14_architecture.tex
revisions

%\begin{itemize}
%\item
There is also an independent store containing all PDS chunks shared among different VMs as
a single file.
%All PDS chunks are stored in one PDS file. 
Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
%There is an option to use a data structure similar to the non-PDS store. We opt
%for the simpler format because
Additional compression is not applied because 
for the data sets we have tested, we only observed limited spatial locality 
among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
Thus it is not very effective to group a large number of chunks as a compression and data fetch unit. 
For the same reason, we decide not to take the sampled index approach~\cite{Guo2011} 
for detecting duplicates from PDS as limited spatial locality is not sufficient to enable
effective prefetching for sampled indexing.

@@

%\item
\noindent\textbf{Delete()}.
Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user and we discuss this in more details in next
subsection.
%(we will discuss the snapshot deletion in detail in the following subsection).
When deletion requests are issued for a specific container,
those requests are simply recorded into the  container's deletion log initially and thus  a lazy
deletion strategy is exercised.
Once local chunk IDs appear in
the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
This is ensured because we only dedup against the direct parent of a snapshot, so the deleted snapshot's blocks
will only be used if they also exist in other snapshots.
Periodically, the snapshot  store picks those containers with an excessive
number of deletion requests to  compact and  reclaim the corresponding disk space. 
During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
existing one. This is done by sequentially scanning the old container, copying all the chunks that are not 
found in the deletion log to the new container, and creating new chunk groups and indices. 
Every local chunk ID however is directly copied rather than re-generated. This
process leaves holes in the chunk ID values, but preserves the order and IDs of chunks.
As a result, all data references stored 
in recipes are permanent and stable, and the data reading process
is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
depend directly on physical storage locations, which simplifies data migration.
%\end{itemize}

@@

\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to  estimation of VM image size,
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.

\item {\bf Approximate deletion with fast summary comparison.}
When there is a snapshot deletion,  
we need to identify if  chunks to be deleted from that snapshot
are still referenced by other snapshots. 
This is done approximately and quickly by comparing the 
reference of deleted chunks  with
the merged Bloom-filter reference summary of other live snapshots.
The merging of live snapshot Bloom-filter bits uses the bitwise OR operator 
and the merged vector still takes $z$ bits.
Since the number of live snapshots $h$ is limited for
each VM, 
the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.

If a chunk's reference is not found in the merged summary vector, we are sure that
this chunk is not used by any live snapshots, thus can be deleted safely.
However, among all the chunks to be deleted, 
there are a small percentage of unused chunks  which
are misjudged as  being in use, resulting in storage leakage.

@@

When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$ we trigger a leak repair. Namely,

>>>>

%\begin{itemize}
%\item
There is an independent store containing all PDS chunks shared among different VMs as
a single file.
%All PDS chunks are stored in one PDS file. 
Each reference to a PDS data chunk in the PDS index is the offset within the PDS file.
%There is an option to use a data structure similar to the non-PDS store. We opt
%for the simpler format because
Additional compression is not applied because 
for the data sets we have tested, we only observed limited spatial locality 
among popular data chunks. On average the number of consecutive PDS index hits is lower than 7.
Thus it is not very effective to group a large number of chunks as a compression and data fetch unit. 
For the same reason, we decide not to take the sampled index approach~\cite{Guo2011} 
for detecting duplicates from PDS as limited spatial locality is not sufficient to enable
effective prefetching for sampled indexing.

@@

%\item
\noindent\textbf{Delete()}.
Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user and we discuss this in more details in next
subsection.
%(we will discuss the snapshot deletion in detail in the following subsection).
When deletion requests are issued for a specific container,
those requests are simply recorded into the  container's deletion log initially and thus  a lazy
deletion strategy is exercised.
Once local chunk IDs appear in
the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
This is ensured because we only dedup against the direct parent of a snapshot, so the deleted snapshot's blocks
will only be used if they also exist in other snapshots.
Periodically, the snapshot  store identifies those containers with an excessive
number of deletion requests to  compact and  reclaim the corresponding disk space. 
During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
existing one. This is done by sequentially scanning the old container, copying all the chunks that are not 
found in the deletion log to the new container, and creating new chunk groups and indices. 
Every local chunk ID however is directly copied rather than re-generated. This
process leaves holes in the chunk ID values, but preserves the order and IDs of chunks.
As a result, all data references stored 
in recipes are permanent and stable, and the data reading process
is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
depend directly on physical storage locations, which simplifies data migration.
%\end{itemize}

@@

\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to  estimation of VM image size,
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
This can be done during the periodic leakage repair stage described below.

\item {\bf Approximate deletion with fast summary comparison.}
When there is a snapshot deletion,  
we need to identify if  chunks to be deleted from that snapshot
are still referenced by other snapshots. 
This is done approximately and quickly by comparing the 
reference of deleted chunks  with
the merged reference summary vectors of other live snapshots.
The merging of live snapshot Bloom-filter vectors uses the bitwise OR operator 
and the merged vector still takes $z$ bits.
Since the number of live snapshots $h$ is limited for
each VM, 
the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.

If a chunk's reference is not found in the merged summary vector, we are sure that
this chunk is not used by any live snapshots, thus it can be deleted safely.
However, among all the chunks to be deleted, 
there are a small percentage of unused chunks  which
are misjudged as  being in use, resulting in storage leakage.

@@

When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we trigger a leak repair. Namely,

### 2013-09-27 snapshot_system/fast14_introduction.tex
revisions

The key contribution is the development and analysis of a VM-centric approach which integrates  multiple duplicate detection strategies
based on changed block tracking, similarity guided local deduplication,
and popularity guided global deduplication. 
This approach localizes duplicate detection within each VM  
and packages only data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience while sustaining competitive deduplication efficiency.
In addition, our VM-centric design allows garbage collection to be performed in a localized
scope and we propose an approximate deletion scheme to reduce this cost further.
Localization also brings the benefits of greater ability to exploit parallelism so
backup operations can run simultaneously without a central  bottleneck.
This VM-centric solution uses a small amount of  memory while delivering reasonable deduplication efficiency.

>>>>

The key contribution of this work is the development and analysis of a VM-centric approach
which considers fault isolation and integrates  multiple duplicate detection strategies
supported by similarity guided local deduplication
and popularity guided global deduplication. 
This approach localizes duplicate detection within each VM  
and packages only data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience while sustaining competitive deduplication efficiency.
In addition, our VM-centric design allows garbage collection to be performed in a localized
scope and we propose an approximate deletion scheme to reduce this cost further.
Localization also brings the benefits of greater ability to exploit parallelism so
backup operations can run simultaneously without a central  bottleneck.
This VM-centric solution uses a small amount of  memory while delivering reasonable deduplication efficiency.
